---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Here is a example of how this package could be used. Let's say there is a statement that you are trying to analyze. This is how you could implement our package.
First you need to import this package with the following command:

```{r setup}
#library(remoodji)
```

Let's say you have the following statement:
`I was happily walking. I then saw a monster and I got scared. However, when I found out it was a prank I became angry instead.`
To start you might want to first determine the number of characters, words, and sentences to ensure that your statement fits within guidelines.

```{r}
remoodji::counter('I was happily walking. I then saw a monster and I got scared. However, when I found out it was a prank I became angry instead.')
```
